\documentclass{hotnets23}

\usepackage{times}  
\usepackage{hyperref}
\usepackage{titlesec}

\hypersetup{pdfstartview=FitH,pdfpagelayout=SinglePage}

\setlength\paperheight {11in}
\setlength\paperwidth {8.5in}
\setlength{\textwidth}{7in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\evensidemargin}{-.25in}

\begin{document}

% \conferenceinfo{HotNets 2023} {}
% \CopyrightYear{2023}
% \crdata{X}
% \date{}

%%%%%%%%%%%% THIS IS WHERE WE PUT IN THE TITLE AND AUTHORS %%%%%%%%%%%%

\title{Project proposal}

\author{Student name}

\maketitle

\section*{Problem statement}
In this section, please define the problem you are trying to solve. Try to add these parts to your description.
\begin{itemize}
\item {\textbf{What is the exact problem you are trying to solve?} Suppose you want to solve the congestion in data center networks.}
\item {\textbf{Why is the problem important?} For example, you can add some statistics from some papers to show that the congestion exists in the datacenters and also, if it decreases it will affect the performance of the network.}
\item {\textbf{Why is the problem hard to solve?} For example, if the congestion in the datacenters can be eliminated by increasing the link capacity, then your problem is not a research problem. The problem you are addressing should have some level of difficulty. (e.g. the congestion in datacenters persist even if we increase the link capacity.)}

\end{itemize}

This section can help you write the introduction of your report at the end of the semester. I suggest you also read R. Levin and DD. Redell 's article \cite{writeAgoodPaper} on how to write a good system paper. It includes some essential questions for you to ask yourself while writing a paper.

\section*{Context}
In this section, please describe your approach to solve the problem in high level overview. You don't need to include details of your solution i.e. codes or detailed design choices but it is best if you name the tools, programming language and environment that you will use. Besides, you should mention the scope of your project, and if Software-Defined Networking (SDN) plays any role in the problem or the solution. Also, you should point out your first steps to attack the problem. These steps can change as you progress in the project.

\section*{Related work}

This section is going to be your search on how other researchers have tried to solve the same problem. If the problem is completely new and no one has thought of it you might find similar problems in other areas rather than networking.

\section*{Acknowledgment}
This template has been borrowed form the HotNets'23 conference.  

\bibliographystyle{abbrv} 
\begin{small}
\bibliography{ref}
\end{small}

\end{document}

